---
title: "Assignment Day 17 - Muh. Hasrun"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Customer_movie_rating.csv contain rating that customers give for each movie genre in a website. Use the data to create a customer segmentation using k-means clustering

2. Pick the best k value according to you and analyze each cluster result


```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(gridExtra)
library(cluster)

```

## Load Data
```{r}
customer_movie_rating <- read.csv("D:/Dibimbing/Day 17/customer_movie_rating.csv", header = T)

head(customer_movie_rating)

```

## Data Preparation

```{r}
df <- na.omit(customer_movie_rating)

df <- scale(customer_movie_rating)

head(df)

```

```{r}
distance <- get_dist(df)

```

## Computing K-Means
```{r}
c2 <- kmeans(df, centers = 2, nstart = 25)
str(c2)

```

## Make more cluster
```{r}
c3 <- kmeans(df, centers = 3, nstart = 25)
c4 <- kmeans(df, centers = 4, nstart = 25)
c5 <- kmeans(df, centers = 5, nstart = 25)

```


## Plot
```{r}
plot1 <- fviz_cluster(c2, geom = "point", data = df) + ggtitle("k = 2")
plot2 <- fviz_cluster(c3, geom = "point", data = df) + ggtitle("k = 3")
plot3 <- fviz_cluster(c4, geom = "point", data = df) + ggtitle("k = 4")
plot4 <- fviz_cluster(c5, geom = "point", data = df) + ggtitle("k = 5")

```

## Compare the plot
```{r}
grid.arrange(plot1, plot2, plot3, plot4, nrow = 2)

```


## Determining Optimal Cluster

### 1. Elbow Method
```{r}
set.seed(123)
fviz_nbclust(df, kmeans, method = "wss")

```

### 2. Silhouette
```{r}
set.seed(123)
fviz_nbclust(df, kmeans, method = "silhouette")

```

### 3. Gap Statistic
```{r}
set.seed(123)
gap_stat <- clusGap(df, FUN = kmeans, nstart = 25,
                    K.max = 10, B = 50)

print(gap_stat, method = "firstmax")
fviz_gap_stat(gap_stat)

```

From the three method used, we can see that the optimal cluster is 2.

## Final Cluster
```{r}
set.seed(123)
final <- kmeans(df, 2, nstart = 25)
final

```

```{r}
customer_movie_rating %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("mean")

```
## Conclusion
By using the K-Means method with 2 clusters, it can be concluded that Cluster 1 consists of 218 customers, most of them like Horror and Action movies, while Cluster 2 consists of 73 customers who mostly like movies with Romcom, Comedy, and Fantasy genres.

