---
title: "Assignment 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Call Package
```{r}
library(tidyverse)

```

## Import Data

```{r}
insurance_loss <- read.csv("D:/Dibimbing/Resources/Insurance_Loss.csv")
glimpse(insurance_loss)

```

## Which gender creates more total loss?

```{r}
ggplot(insurance_loss,aes(x=insurance_loss$Gender,y=insurance_loss$Losses)) + geom_point()

```
Although there are more females than males, but the amount of losses caused by males is more than females.

## Which status creates more total loss?

```{r}
ggplot(insurance_loss,aes(x=insurance_loss$Married,y=insurance_loss$Losses)) + geom_point()

```
Single have higher total losses than married. Most of those who are married are more mature and cautious in driving. 

## Which type of fuel creates more total loss?

```{r}
ggplot(insurance_loss,aes(x=insurance_loss$Fuel.Type,y=insurance_loss$Losses)) + geom_point()

```
In terms of strength, diesel engine performance is superior to petroleum engines. Also, the potential for petroleum engine to burn is greater than diesel engine.

## Graph Boxplot

```{r}
ggplot(insurance_loss,aes(x=insurance_loss$Gender,y=insurance_loss$Age)) + geom_boxplot(aes(color = insurance_loss$Gender))

```

```{r}
ggplot(data=mpg,aes(x=displ,y=hwy,color="blue")) + geom_point()

```
the point not turns to blue because the word color must inside geom_point()
